Clustering in a hyperbolic model of complex networks.

### 2019-02-27 concentration.tex
finished section 8.2

Recall the adjusted triangle count function
\[
	\widetilde{T}_{\text{box}}(p_0) = \sum_{(p_1, p_2) \in \Pcal \setminus p_0}^{\ne} 
		\widetilde{T}_{\text{box}}(p_0,p_1,p_2).
\]
where
\[
	\widetilde{T}_{\text{box}}(p_0,p_1,p_2) = \ind{p_1 \in \BallPon{p}}\ind{p_2 \in \BallPon{p}}\ind{p_2 \in \BallPo{p_1} \cap \Rcal},
\]
and recall the definition of $\Kcal_{C,n}(k_n)$
\[
	\Kcal_{C,n}(k_n) = \left\{p \in \Rcal : \frac{k_n - C \sqrt{k_n \log(k_n)}}{\xi} \vee 1 \le e^{\frac{y}{2}}
		\le \frac{k_n + C \sqrt{k_n \log(k_n)}}{\xi} \right\}.
\]

Slightly abusing notation, we will define the corresponding triangle degree function
\begin{equation}\label{eq:def_degree_triangle_count_in_K}
	\widetilde{T}_{\text{box}}(k, C) = \sum_{p \in \Pcal_n \cap \Kcal_{C,n}(k_n)} \ind{\text{deg}_{\text{box}}(p) = k} \widetilde{T}_{\text{box}}(p).
\end{equation}
The idea is that the main contribution of triangles of degree $k_n$ is given by $\widetilde{T}_{\text{box}}(k_n, C)$. Therefore, in order to prove Proposition \ref{prop:concentration_local_clustering_P_n} it suffices to show that $\widetilde{T}_{\text{box}}(k_n,C)$ is sufficiently concentrated around its mean. This is done in the following proposition.

@@

We start with analyzing joint neighborhoods in $\Gbox$. Let $p, p^\prime \in \Rcal$. Then we denote by $\Ncal_{\text{box}}(p\Delta p^\prime)$ the number of disjoint neighbors of $p$ and $p^\prime$ in $\Gbox$, i.e. those points that belong to either $\BallPon{p}$ or $\BallPon{p^\prime}$ but not to their intersection. In addition we denote by $\Ncal_{\text{box}}(p,p^\prime)$ the number of joint neighbors of $p$ and $p^\prime$. We shall establish lower bounds on the expected number of these disjoint neighbors $\Exp{\Ncal_{\text{box}}(p\Delta p^\prime)}$ as well as an asymptotic expression for the expected number of joint neighbors. For this we will distinguish between the cases where the distance between the $x$-coordinates of $p$ and $p^\prime$ is small or large. Figure~\ref{fig:representation_disjoint_neighborhoods_P_n}-\ref{fig:representation_disjoint_neighborhoods_P_n_3} show the different situations that occur.

@@

    \draw node at (-7,0.8563) {$h(p,p^\prime)$};
    \draw node at (7,0.3109) {\color{blue}$h_1(p^\prime)$};

@@

    \draw [dotted,line width=1pt] (2.5298,0.8563) -- (2.5298,1.7);
    \draw node at (2.5298,2) {$x^\ast(p,p^\prime)$};

@@

We start by analyzing the shape of the neighborhoods. Due to symmetry and the fact that we have identified the left and right boundaries of the box $\Rcal$, we can, without loss of generality, assume that $p = (0,y)$ and $p^\prime = (x^\prime,y^\prime)$ with $x^\prime > 0$ and $y^\prime \le y$. To understand the computation it is helpful to have a picture of the different situations. Figure \ref{fig:representation_disjoint_neighborhoods_P_n} and Figure \ref{fig:representation_disjoint_neighborhoods_P_n_2} show two different situations for small distance in the $x$-coordinates, in which case the number of disjoint neighbors is small. The case where this distance is large, and the number of disjoint neighbors is expected to be large, is shown in Figure \ref{fig:representation_disjoint_neighborhoods_P_n_3}. There are several different quantities that are important. The first are the heights $h_1(p^\prime)$ and $h_2(p^\prime)$ where, respectively, the left and right boundaries of the ball $\BallPon{p^\prime}$ go outside the box $\Rcal$. Note that when $x = 0$ then these heights are the same and we denote this by $h(y)$. We also need to know the coordinates $h(p,p^\prime)$ and $x^\ast(p,p^\prime)$ of the intersection of the right boundary of the neighborhood of $p$ with the left boundary of the neighborhood of $p^\prime$. Finally we will denote by $d(p,p^\prime)$ the distance between the lower right boundary of $\BallPon{p}$ and the lower left of $\BallPon{p^\prime}$, which is positive only when the bottom parts of both neighborhoods do not intersect, compare Figures \ref{fig:representation_disjoint_neighborhoods_P_n} and \ref{fig:representation_disjoint_neighborhoods_P_n_3}. The full expressions of all these functions are given below for further reference.

\begin{align}
	h(y) &= R_n - y + 2\log\left(\frac{\pi}{2}\right) \label{eq:def_height_y_P_n}\\
	h_1(p^\prime) &= 2\log\left(x^\prime + \frac{\pi}{2}e^{\frac{R_n}{2}}\right) - y^\prime \label{eq:def_height_left_P_n} \\
	h_2(p^\prime) &= 2\log\left(\frac{\pi}{2}e^{\frac{R_n}{2}} - x^\prime\right) - y^\prime 
		\label{eq:def_height_right_P_n} \\
%	\iota_x(p,p^\prime) &= \frac{(x^\prime-x)e^{\frac{y}{2}}}{e^{\frac{y}{2}} - e^{\frac{y^\prime}{2}}}
%		\label{eq:def_x_intersection_close_boundaries}\\
%	\iota_y(p,p^\prime) &= 2\log\left(\frac{x^\prime - x}{e^{\frac{y}{2}} - e^{\frac{y^\prime}{2}}}\right)
%		\label{eq:def_y_intersection_close_boundaries}\\
	h(p,p^\prime) &= 2\log\left(\frac{|x - x^\prime|}{e^{\frac{y}{2}} + e^{\frac{y^\prime}{2}}}\right)\\
	x^\ast(p,p^\prime) &= \frac{x e^{\frac{y^\prime}{2}} + x^\prime e^{\frac{y}{2}}}{e^{\frac{y}{2}} + 	
		e^{\frac{y^\prime}{2}}},\\
	d(p,p^\prime) &= |x - x^\prime| - \left(e^{\frac{y}{2}} + e^{\frac{y^\prime}{2}}\right).
	\label{eq:def_d_p_p_prime}
\end{align}

@@

\begin{lemma}\label{lem:disjoint_neighbors_P_n}
Let $p, p ^\prime \in \Rcal$. Then whenever $|x - x^\prime| \le e^{\frac{y}{2}} + e^{\frac{y^\prime}{2}}$,
\begin{align*}
	\Exp{\Ncal_{\text{box}}(p \Delta p^\prime)}
	&\ge \frac{\nu}{\pi}|x^\prime - x|\left(1 - \left(\frac{2}{\pi}\right)^{2\alpha}e^{-\alpha(R_n - y^\ast)}\right)\\
	&\hspace{10pt}+ \xi_{\alpha, \nu}\left|e^{\frac{y}{2}} - e^{\frac{y^\prime}{2}}\right|
		\left(1 - \left(\frac{2}{\pi}\right)^{2\alpha - 1}e^{-(\alpha - \frac{1}{2})(R_n-y^\ast)}\right).
\end{align*}
\end{lemma}

@@

By the Campbell-Mecke formula we get
\begin{align*}
	\Exp{\Ncal_{\text{box}}(p \Delta p^\prime)} &=	\Mu{\BallPon{p} \Delta B_{\Pcal,n}(p^\prime)}\\
	&\ge \int_0^{h^\ast} \int_{x - e^{\frac{y + y_1}{2}}}^{x^\prime - e^{\frac{y^\prime + y_1}{2}}} f(x_1,y_1)
		\, dx_1 \, dy_1 \\
	&= \frac{\alpha \nu}{\pi}|x^\prime - x| \int_{0}^{h^\ast} e^{-\alpha y_1} dy_1
		+ \frac{\alpha \nu}{\pi}\left|e^{\frac{y}{2}} - e^{\frac{y^\prime}{2}}\right| \int_0^{h^\ast} 
		e^{-(\alpha-\frac{1}{2})y_1} \, dy_1\\
	&= \frac{\nu}{\pi}|x^\prime - x|\left(1 - \left(\frac{2}{\pi}\right)^{2\alpha}e^{-\alpha(R_n - y^\ast)}\right)\\
	&\hspace{10pt}+ \xi_{\alpha, \nu}\left|e^{\frac{y}{2}} - e^{\frac{y^\prime}{2}}\right|
		\left(1 - \left(\frac{2}{\pi}\right)^{2\alpha - 1}e^{-(\alpha - \frac{1}{2})(R_n-y^\ast)}\right).
\end{align*}
\end{proof}

@@

\[
	\phi_n(p,p^\prime) = \xi_{\alpha, \nu}\left( \left(\frac{e^{y/2} + e^{y^\prime/2}}{|x-x^\prime|}\right)^{2\alpha - 1}
	- e^{-(\alpha - \frac{1}{2})R_n}\right)
\]
\end{lemma}

\begin{proof}
We will prove the results by using that
\[
	\Exp{\Ncal_{\text{box}}(p\Delta p^\prime)} 
	\ge \int_0^{h(p,p^\prime)} \int_{-\frac{\pi}{2}e^{\frac{R_n}{2}}}^{\frac{\pi}{2}e^{\frac{R_n}{2}}} \ind{p_1 \in \BallPon{p} \cup \BallPon{p^\prime}} f(x_1,y_1) \, dx_1 \, dy_1,
\]
and computing the integral on the right. We refer to Figure~\ref{fig:representation_disjoint_neighborhoods_P_n_3} for further clarification.

Before we proceed we show that the neighborhoods of $p$ and $p^\prime$ below $h(p,p^\prime)$ are disjoint. This is clearly true when $h(p,p^\prime) \le h_2(p^\prime)$ so suppose that $h(p,p^\prime) > h_2(p^\prime)$. Then, because we identified the right and left boundaries of the box $\Rcal$ the right boundary of $\BallPon{p^\prime}$ continues from the left boundary of the box and is described by the equation
\[
	x_1 = x^\prime + e^{\frac{y^\prime + y_1}{2}} - \pi e^{\frac{R_n}{2}}.
\]
Now, let $x_{\mathrm{right}}^\prime$ and $x_{\mathrm{left}}$ denote the $x$-coordinate of the intersection of the line $h(p,p^\prime)$ with, respectively, the right boundary of $\BallPon{p^\prime}$ and the left boundary of $\BallPon{p}$. Then
\begin{align*}
	x_{\mathrm{right}}^\prime &= x^\prime + e^{\frac{y^\prime + h(p,p^\prime)}{2}} - \pi e^{\frac{R_n}{2}}\\
	&= x^\prime + e^{\frac{h(p,p^\prime)}{2}}\left(e^{\frac{y}{2}} + e^{\frac{y^\prime}{2}}\right)
		- e{\frac{y + h(p,p^\prime)}{2}} - \pi e^{\frac{R_n}{2}}\\
	&= x^\prime + |x - x^\prime| - e{\frac{y + h(p,p^\prime)}{2}} - \pi e^{\frac{R_n}{2}}\\
	&= x - e{\frac{y + h(p,p^\prime)}{2}} + 2|x - x^\prime| - \pi e^{\frac{R_n}{2}}\\
	&\le x - e{\frac{y + h(p,p^\prime)}{2}} = x_{\mathrm{right}},
\end{align*}
and hence the neighborhoods of $p$ and $p^\prime$ below $h(p,p^\prime)$ are disjoint. It then follows that
\begin{align*}
	\Exp{\Ncal_{\text{box}}(p,p^\prime)} 
	&\ge \int_0^{h(p,p^\prime)} \int_{-\frac{\pi}{2}e^{\frac{R_n}{2}}}^{\frac{\pi}{2}e^{\frac{R_n}{2}}} 
		\ind{p_1 \in \BallPon{p} \cup \BallPon{p^\prime}} f(x_1,y_1) \, dx_1 \, dy_1\\
	&= \int_0^{h(p,p^\prime)} \int_{-\frac{\pi}{2}e^{\frac{R_n}{2}}}^{\frac{\pi}{2}e^{\frac{R_n}{2}}} 
		\left(\ind{p_1 \in \BallPon{p}} + \ind{p_1 \in \BallPon{p^\prime}}\right) 
		f(x_1,y_1) \, dx_1 \, dy_1\\
	&= \left(\mu_{\alpha,\nu ,n}(\BallPon{p}) + \mu_{\alpha,\nu ,n}(\BallPon{p^\prime})\right)
		\left(1 - \frac{2\alpha \nu}{\pi}\int_{h(p,p^\prime)}^{R_n} e^{-(\alpha - \frac{1}{2})y_1} \, dy_1\right),
\end{align*}
from which the result follows since
\begin{align*}
	\frac{2\alpha \nu}{\pi}\int_{h(p,p^\prime)}^{R_n} e^{-(\alpha - \frac{1}{2})y_1} \, dy_1 
	&= \xi_{\alpha, \nu}\left(e^{-(\alpha - \frac{1}{2})h(p,p^\prime)} - e^{-(\alpha - \frac{1}{2})R_n}\right)\\
	&= \xi_{\alpha, \nu}\left(\left(\frac{e^{y/2} + e^{y^\prime/2}}{|x-x^\prime|}\right)^{2\alpha - 1}
		- e^{-(\alpha - \frac{1}{2})R_n}\right).
\end{align*}
\end{proof}

@@

Next we consider the number of common neighbors between two nodes $p$ and $p^\prime$ in $\Ginf$, which we denote by $\Ncal_{\Pcal}(p,p^\prime)$.

@@

For the first term we get
\begin{align*}
	&\hspace{-30pt}\left(e^{y/2} + e^{y^\prime/2}\right)\frac{\alpha \nu}{\pi}\int_{h(p,p^\prime)}^{R_n} 
		e^{-(\alpha - \frac{1}{2})y_1} \dd y_1\\
	&= \xi_{\alpha, \nu}\left(e^{y/2} + e^{y^\prime/2}\right)\left(
		e^{-(\alpha - \frac{1}{2})h(p,p^\prime)} - e^{-(\alpha - \frac{1}{2})R_n}\right)\\
	&= \xi_{\alpha, \nu}\left(e^{y/2} + e^{y^\prime/2}\right)\left(\left(\frac{|x^\prime - x|}{e^{y/2} + 	
		e^{y^\prime/2}}\right)^{-(2\alpha - 1)} - e^{-(\alpha - \frac{1}{2})R_n}\right).
\end{align*}
For the other term we compute
\begin{align*}
	&\hspace{-30pt}(x^\prime - x) \frac{\alpha \nu}{\pi} \int_{h(p,p^\prime)}^{R_n} e^{-\alpha y_1} \dd y_1\\
	&= (x^\prime - x) \frac{\nu}{\pi}\left(e^{-\alpha(p,p^\prime)} - e^{-\alpha R_n}\right)\\
	&= \frac{\nu}{\pi}\left(e^{y/2} + e^{y^\prime/2}\right) \left(
		\left(\frac{|x^\prime - x|}{e^{y/2} + e^{y^\prime/2}}\right)^{-(2\alpha - 1)}
		- (x^\prime - x)e^{-\alpha R_n}\right)\\
	&= \xi_{\alpha, \nu}\left(e^{y/2} + e^{y^\prime/2}\right)\left(
		\frac{2\alpha - 1}{4\alpha}\left(\frac{|x^\prime - x|}{e^{y/2} + e^{y^\prime/2}}\right)^{-(2\alpha - 1)}
		- \frac{2\alpha - 1}{4\alpha}|x^\prime - x|e^{-\alpha R_n}\right).
\end{align*}
Combining these two results and noticing that $\xi_{\alpha, \nu} e^{y/2} = \Mu{\BallPon{p}}$ and similar for $p^\prime$ finishes the proof.
\end{proof}

@@

We now turn to the joint degree distribution of nodes in $\Gbox$. To ease notations we introduce the following short-hand notation for the conditional joint degree distribution
\[
	\rho_n(p,p^\prime,k,k^\prime) 
	:= \Prob{D_{\Pcal,n}(p) = k, D_{\Pcal,n}(p^\prime) = k^\prime}.
\]

We first establish an almost independence result for integrals over the joint degree distribution $\rho_{n}(p,p^\prime,k,k^\prime)$ for the case where  $p$ and $p^\prime$ are sufficiently separated. For this we note that when $|x - x^\prime| \gg e^{y/2} + e^{y^\prime/2}$ it follows from Lemma~\ref{lem:disjoint_neighbors_P_n_large}
\[
	\Exp{\Ncal_{\text{box}}(p \Delta p^\prime)} = \left(\Mu{\BallPon{p}} + \Mu{\BallPon{p^\prime}}\right)(1 + \smallO{1}),
\] 
for $p, p^\prime \in \Kcal_{C}(k_n) \times \Kcal_{C}(k_n)$. This implies that the joint neighborhoods are almost independent and hence their degrees must be as well. To make this more precise, let $0 < \varepsilon < \min\{(2\alpha - 1)^{-1},1\}$ and define the following two sets
\begin{align}
	\mathcal{E}(k_n) &= \left\{(p,p^\prime) \in \Kcal_C(k_n) \times \Kcal_C(k_n) 
			\, : \, |x - x^\prime| > \left(e^{y/2} + e^{y^\prime/2}\right) \log(n)
		\right\} \label{eq:def_joint_degree_set_E_constant_k} \\
	\mathcal{E}_{\varepsilon}(k_n) &= \left\{(p,p^\prime) \in \Kcal_C(k_n) \times \Kcal_C(k_n) 
		\, : \, \Exp{\Ncal_{\text{box}}(p, p^\prime)} \ge k_n^{\varepsilon} \text{ and } |x - x^\prime| > k_n^{1 + \varepsilon} \right\}. \label{eq:def_joint_degree_set_E_growing_k}
\end{align}

@@

	\phi_n(p,p^\prime) 

>>>>

First we write
\[
	c^\ast(k_n ; \Gbox) = \frac{T_{\text{box}}(k_n)}{\binom{k_n}{2}\Exp{\Nbox(k_n)}},
\]
where
\[
	 T_{\text{box}}(k_n) = \sum_{p \in \Pcal} \ind{\Dbox(p) = k_n} \sum_{p_1, p_2 \in \Pcal \setminus p}^{\ne} 
	 \ind{p_1 \in \BallPon{p}}\ind{p_2 \in \BallPon{p}}\ind{p_2 \in \BallPon{p_1}}
\]
In particular, the variance of $c^\ast(k_n ; \Gbox)$ is determined by the variance of $T_{\text{box}}(k_n)$.

Next, recall the adjusted triangle count function
\[
	\widetilde{T}_{\text{box}}(p_0) = \sum_{(p_1, p_2) \in \Pcal \setminus p_0}^{\ne} 
		\widetilde{T}_{\text{box}}(p_0,p_1,p_2).
\]
where
\[
	\widetilde{T}_{\text{box}}(p_0,p_1,p_2) = \ind{p_1 \in \BallPon{p_0}}\ind{p_2 \in \BallPon{p_0}}\ind{p_2 \in \BallPo{p_1} \cap \Rcal},
\]
and recall the definition of $\Kcal_{C,n}(k_n)$
\[
	\Kcal_{C,n}(k_n) = \left\{p \in \Rcal : \frac{k_n - C \sqrt{k_n \log(k_n)}}{\xi} \vee 1 \le e^{\frac{y}{2}}
		\le \frac{k_n + C \sqrt{k_n \log(k_n)}}{\xi} \right\}.
\]
Slightly abusing notation, we will define the corresponding triangle degree function
\begin{equation}\label{eq:def_degree_triangle_count_in_K}
	\widetilde{T}_{\text{box}}(k, C) = \sum_{p \in \Pcal \cap \Kcal_{C,n}(k_n)} \ind{\text{deg}_{\text{box}}(p) = k} \widetilde{T}_{\text{box}}(p).
\end{equation}
The idea is that the main contribution of triangles of degree $k_n$ to $T_{\text{box}}(k_n)$ is given by $\widetilde{T}_{\text{box}}(k_n, C)$. Therefore, in order to prove Proposition \ref{prop:concentration_local_clustering_P_n} it suffices to show that $\widetilde{T}_{\text{box}}(k_n,C)$ is sufficiently concentrated around its mean. This is done in the following proposition.

@@

We start with analyzing joint neighborhoods in $\Gbox$. Let $p, p^\prime \in \Rcal$. Then we denote by $\Ncal_{\text{box}}(p\Delta p^\prime)$ the number of disjoint neighbors of $p$ and $p^\prime$ in $\Gbox$, i.e. those points that belong to either $\BallPon{p}$ or $\BallPon{p^\prime}$ but not to their intersection. In addition we denote by $\Ncal_{\text{box}}(p,p^\prime)$ the number of joint neighbors of $p$ and $p^\prime$. We shall establish lower bounds on the expected number of points in the disjoint neighborhood $\Exp{\Ncal_{\text{box}}(p\Delta p^\prime)}$ as well as an asymptotic expression for the expected number points in the joint neighborhood. For this we will distinguish between the cases where the distance between the $x$-coordinates of $p$ and $p^\prime$ is small or large. Figure~\ref{fig:representation_disjoint_neighborhoods_P_n}-\ref{fig:representation_disjoint_neighborhoods_P_n_3} show the different situations that occur.

@@

    \draw node at (-7,0.8563) {$\hat{y}(p,p^\prime)$};
    \draw node at (7,0.3109) {\color{blue}$h_1(p^\prime)$};

@@

    \draw [dotted,line width=1pt] (2.5298,0.8563) -- (2.5298,1.7);
    \draw node at (2.5298,2) {$\hat{x}(p,p^\prime)$};

@@

We start by analyzing the shape of the neighborhoods. Due to symmetry and the fact that we have identified the left and right boundaries of the box $\Rcal$, we can, without loss of generality, assume that $p = (0,y)$ and $p^\prime = (x^\prime,y^\prime)$ with $x^\prime > 0$ and $y^\prime \le y$. To understand the computation it is helpful to have a picture of the different situations. Figure \ref{fig:representation_disjoint_neighborhoods_P_n} and Figure \ref{fig:representation_disjoint_neighborhoods_P_n_2} show two different situations for small distance in the $x$-coordinates, in which case the number of disjoint neighbors is small. The case where this distance is large, and hence the number of disjoint neighbors is expected to be large, is shown in Figure \ref{fig:representation_disjoint_neighborhoods_P_n_3}. There are several different quantities that are important. The first are the heights $h_1(p^\prime)$ and $h_2(p^\prime)$ where, respectively, the left and right boundaries of the ball $\BallPon{p^\prime}$ go outside the box $\Rcal$. Note that when $x = 0$ then these heights are the same and we denote this by $h(y)$. We also need to know the coordinates $\hat{y}(p,p^\prime)$ and $\hat{x}(p,p^\prime)$ of the intersection of the right boundary of the neighborhood of $p$ with the left boundary of the neighborhood of $p^\prime$. Finally we will denote by $d(p,p^\prime)$ the distance between the lower right boundary of $\BallPon{p}$ and the lower left of $\BallPon{p^\prime}$, which is positive only when the bottom parts of both neighborhoods do not intersect, compare Figures \ref{fig:representation_disjoint_neighborhoods_P_n} and \ref{fig:representation_disjoint_neighborhoods_P_n_3}. The derivation of the expression for these functions is similar to those in Section~\ref{ssec:missing_triangles} and we omit the details here. The full expressions of all these functions are given below for further reference.

\begin{align}
	h(y) &= R_n - y + 2\log\left(\frac{\pi}{2}\right) \label{eq:def_height_y_P_n}\\
	h_1(p^\prime) &= 2\log\left(x^\prime + \frac{\pi}{2}e^{\frac{R_n}{2}}\right) - y^\prime \label{eq:def_height_left_P_n} \\
	h_2(p^\prime) &= 2\log\left(\frac{\pi}{2}e^{\frac{R_n}{2}} - x^\prime\right) - y^\prime 
		\label{eq:def_height_right_P_n} \\
%	\iota_x(p,p^\prime) &= \frac{(x^\prime-x)e^{\frac{y}{2}}}{e^{\frac{y}{2}} - e^{\frac{y^\prime}{2}}}
%		\label{eq:def_x_intersection_close_boundaries}\\
%	\iota_y(p,p^\prime) &= 2\log\left(\frac{x^\prime - x}{e^{\frac{y}{2}} - e^{\frac{y^\prime}{2}}}\right)
%		\label{eq:def_y_intersection_close_boundaries}\\
	\hat{y}(p,p^\prime) &= 2\log\left(\frac{|x - x^\prime|}{e^{\frac{y}{2}} + e^{\frac{y^\prime}{2}}}\right)\\
	\hat{x}(p,p^\prime) &= \frac{x e^{\frac{y^\prime}{2}} + x^\prime e^{\frac{y}{2}}}{e^{\frac{y}{2}} + 	
		e^{\frac{y^\prime}{2}}},\\
	d(p,p^\prime) &= |x - x^\prime| - \left(e^{\frac{y}{2}} + e^{\frac{y^\prime}{2}}\right).
	\label{eq:def_d_p_p_prime}
\end{align}

@@

\begin{lemma}\label{lem:disjoint_neighbors_P_n}
Let $p, p ^\prime \in \Rcal$ and denote $y^\ast = \min\{y, y^\prime\}$. Then whenever $|x - x^\prime| \le e^{\frac{y}{2}} + e^{\frac{y^\prime}{2}}$,
\begin{align*}
	\Exp{\Ncal_{\text{box}}(p \Delta p^\prime)}
	&\ge \frac{\nu}{\pi}|x^\prime - x|\left(1 - \left(\frac{2}{\pi}\right)^{2\alpha}e^{-\alpha(R_n - y^\ast)}\right)\\
	&\hspace{10pt}+ \xi\left|e^{\frac{y}{2}} - e^{\frac{y^\prime}{2}}\right|
		\left(1 - \left(\frac{2}{\pi}\right)^{2\alpha - 1}e^{-(\alpha - \frac{1}{2})(R_n-y^\ast)}\right).
\end{align*}
\end{lemma}

@@

By the Campbell-Mecke formula we get
\begin{align*}
	\Exp{\Ncal_{\text{box}}(p \Delta p^\prime)} &=	\Mu{\BallPon{p} \Delta B_{\Pcal,n}(p^\prime)}\\
	&\ge \int_0^{h^\ast} \int_{x - e^{\frac{y + y_1}{2}}}^{x^\prime - e^{\frac{y^\prime + y_1}{2}}} f(x_1,y_1)
		\, dx_1 \, dy_1 \\
	&= \frac{\alpha \nu}{\pi}|x^\prime - x| \int_{0}^{h^\ast} e^{-\alpha y_1} dy_1
		+ \frac{\alpha \nu}{\pi}\left|e^{\frac{y}{2}} - e^{\frac{y^\prime}{2}}\right| \int_0^{h^\ast} 
		e^{-(\alpha-\frac{1}{2})y_1} \, dy_1\\
	&= \frac{\nu}{\pi}|x^\prime - x|\left(1 - \left(\frac{2}{\pi}\right)^{2\alpha}e^{-\alpha(R_n - y^\ast)}\right)\\
	&\hspace{10pt}+ \xi\left|e^{\frac{y}{2}} - e^{\frac{y^\prime}{2}}\right|
		\left(1 - \left(\frac{2}{\pi}\right)^{2\alpha - 1}e^{-(\alpha - \frac{1}{2})(R_n-y^\ast)}\right).
\end{align*}
\end{proof}

@@

\[
	\phi_n(p,p^\prime) = \xi\left( \left(\frac{e^{y/2} + e^{y^\prime/2}}{|x-x^\prime|}\right)^{2\alpha - 1}
	- e^{-(\alpha - \frac{1}{2})R_n}\right)
\]
\end{lemma}

\begin{proof}
We will prove the results by using that
\[
	\Exp{\Ncal_{\text{box}}(p\Delta p^\prime)} 
	\ge \int_0^{\hat{y}(p,p^\prime)} \int_{-\frac{\pi}{2}e^{\frac{R_n}{2}}}^{\frac{\pi}{2}e^{\frac{R_n}{2}}} \ind{p_1 \in \BallPon{p} \cup \BallPon{p^\prime}} f(x_1,y_1) \, dx_1 \, dy_1,
\]
and computing the integral on the right. We refer to Figure~\ref{fig:representation_disjoint_neighborhoods_P_n_3} for further clarification.

Before we proceed we show that the neighborhoods of $p$ and $p^\prime$ below $\hat{y}(p,p^\prime)$ are disjoint. This is clearly true when $\hat{y}(p,p^\prime) \le h_2(p^\prime)$ so suppose that $\hat{y}(p,p^\prime) > h_2(p^\prime)$. Then, because we identified the right and left boundaries of the box $\Rcal$ the right boundary of $\BallPon{p^\prime}$ continues from the left boundary of the box and is described by the equation
\[
	x_1 = x^\prime + e^{\frac{y^\prime + y_1}{2}} - \pi e^{\frac{R_n}{2}}.
\]
Now, let $x_{\mathrm{right}}^\prime$ and $x_{\mathrm{left}}$ denote the $x$-coordinate of the intersection of the line $\hat{y}(p,p^\prime)$ with, respectively, the right boundary of $\BallPon{p^\prime}$ and the left boundary of $\BallPon{p}$. Then
\begin{align*}
	x_{\mathrm{right}}^\prime &= x^\prime + e^{\frac{y^\prime + \hat{y}(p,p^\prime)}{2}} - \pi e^{\frac{R_n}{2}}\\
	&= x^\prime + e^{\frac{\hat{y}(p,p^\prime)}{2}}\left(e^{\frac{y}{2}} + e^{\frac{y^\prime}{2}}\right)
		- e^{\frac{y + \hat{y}(p,p^\prime)}{2}} - \pi e^{\frac{R_n}{2}}\\
	&= x^\prime + |x - x^\prime| - e{\frac{y + \hat{y}(p,p^\prime)}{2}} - \pi e^{\frac{R_n}{2}}\\
	&= x - e^{\frac{y + \hat{y}(p,p^\prime)}{2}} + 2|x - x^\prime| - \pi e^{\frac{R_n}{2}}\\
	&\le x - e^{\frac{y + \hat{y}(p,p^\prime)}{2}} = x_{\mathrm{left}},
\end{align*}
and hence the neighborhoods of $p$ and $p^\prime$ below $\hat{y}(p,p^\prime)$ are disjoint. It then follows that
\begin{align*}
	\Exp{\Ncal_{\text{box}}(p,p^\prime)} 
	&\ge \int_0^{\hat{y}(p,p^\prime)} \int_{-\frac{\pi}{2}e^{\frac{R_n}{2}}}^{\frac{\pi}{2}e^{\frac{R_n}{2}}} 
		\ind{p_1 \in \BallPon{p} \cup \BallPon{p^\prime}} f(x_1,y_1) \, dx_1 \, dy_1\\
	&= \int_0^{\hat{y}(p,p^\prime)} \int_{-\frac{\pi}{2}e^{\frac{R_n}{2}}}^{\frac{\pi}{2}e^{\frac{R_n}{2}}} 
		\left(\ind{p_1 \in \BallPon{p}} + \ind{p_1 \in \BallPon{p^\prime}}\right) 
		f(x_1,y_1) \, dx_1 \, dy_1\\
	&= \left(\mu_{\alpha,\nu ,n}(\BallPon{p}) + \mu_{\alpha,\nu ,n}(\BallPon{p^\prime})\right)
		\left(1 - \frac{2\alpha \nu}{\pi}\int_{\hat{y}(p,p^\prime)}^{R_n} e^{-(\alpha - \frac{1}{2})y_1} \, dy_1\right),
\end{align*}
from which the result follows since
\begin{align*}
	\frac{2\alpha \nu}{\pi}\int_{\hat{y}(p,p^\prime)}^{R_n} e^{-(\alpha - \frac{1}{2})y_1} \, dy_1 
	&= \xi\left(e^{-(\alpha - \frac{1}{2})\hat{y}(p,p^\prime)} - e^{-(\alpha - \frac{1}{2})R_n}\right)\\
	&= \xi\left(\left(\frac{e^{y/2} + e^{y^\prime/2}}{|x-x^\prime|}\right)^{2\alpha - 1}
		- e^{-(\alpha - \frac{1}{2})R_n}\right).
\end{align*}
\end{proof}

@@

Next we consider the number of common neighbors between two nodes $p$ and $p^\prime$ in $\Gbox$, which we denote by $\Ncal_{\Pcal}(p,p^\prime)$.

@@

For the first term we get
\begin{align*}
	&\hspace{-30pt}\left(e^{y/2} + e^{y^\prime/2}\right)\frac{\alpha \nu}{\pi}\int_{h(p,p^\prime)}^{R_n} 
		e^{-(\alpha - \frac{1}{2})y_1} \dd y_1\\
	&= \xi\left(e^{y/2} + e^{y^\prime/2}\right)\left(
		e^{-(\alpha - \frac{1}{2})h(p,p^\prime)} - e^{-(\alpha - \frac{1}{2})R_n}\right)\\
	&= \xi\left(e^{y/2} + e^{y^\prime/2}\right)\left(\left(\frac{|x^\prime - x|}{e^{y/2} + 	
		e^{y^\prime/2}}\right)^{-(2\alpha - 1)} - e^{-(\alpha - \frac{1}{2})R_n}\right).
\end{align*}
For the other term we compute
\begin{align*}
	&\hspace{-30pt}(x^\prime - x) \frac{\alpha \nu}{\pi} \int_{h(p,p^\prime)}^{R_n} e^{-\alpha y_1} \dd y_1\\
	&= (x^\prime - x) \frac{\nu}{\pi}\left(e^{-\alpha(p,p^\prime)} - e^{-\alpha R_n}\right)\\
	&= \frac{\nu}{\pi}\left(e^{y/2} + e^{y^\prime/2}\right) \left(
		\left(\frac{|x^\prime - x|}{e^{y/2} + e^{y^\prime/2}}\right)^{-(2\alpha - 1)}
		- (x^\prime - x)e^{-\alpha R_n}\right)\\
	&= \xi\left(e^{y/2} + e^{y^\prime/2}\right)\left(
		\frac{2\alpha - 1}{4\alpha}\left(\frac{|x^\prime - x|}{e^{y/2} + e^{y^\prime/2}}\right)^{-(2\alpha - 1)}
		- \frac{2\alpha - 1}{4\alpha}|x^\prime - x|e^{-\alpha R_n}\right).
\end{align*}
Combining these two results and noticing that $\xi e^{y/2} = \Mu{\BallPon{p}}$ and similar for $p^\prime$ finishes the proof.
\end{proof}

@@

We now turn to the joint degree distribution of nodes in $\Gbox$. To ease notations we introduce the following short-hand notation for the joint degree distribution
\[
	\rho_{\text{box}}(p,p^\prime,k,k^\prime) 
	:= \Prob{\Po\left(\Mu{\BallPon{p}}\right) = k, \Po\left(\Mu{\BallPon{p^\prime}}\right) = k^\prime}.
\]

We first establish an almost independence result for integrals over the joint degree distribution $\rho_{\text{box}}(p,p^\prime,k,k^\prime)$ for the case where  $p$ and $p^\prime$ are sufficiently separated. For this we note that when $|x - x^\prime| \gg e^{y/2} + e^{y^\prime/2}$ it follows from Lemma~\ref{lem:disjoint_neighbors_P_n_large}
\[
	\Exp{\Ncal_{\text{box}}(p \Delta p^\prime)} = \left(\Mu{\BallPon{p}} + \Mu{\BallPon{p^\prime}}\right)(1 + \smallO{1}),
\] 
for $p, p^\prime \in \Kcal_{C}(k_n) \times \Kcal_{C}(k_n)$. This implies that the joint neighborhoods are almost independent and hence their degrees must be as well. To make this more precise, let $0 < \varepsilon < \min\{(2\alpha - 1)^{-1},1\}$ and define the following set
\begin{align}
	\mathcal{E}_{\varepsilon}(k_n) &= \left\{(p,p^\prime) \in \Rcal \times \Rcal
		\, : \, y,y^\prime \in \Kcal_{C}(k_n) \text{ and } |x - x^\prime| > k_n^{1 + \varepsilon} \right\}. \label{eq:def_joint_degree_set_E_growing_k}
\end{align}

@@

	X_1(p,p^\prime) &:= \Po\left(\Mu{\BallPon{p}\setminus \BallPon{p^\prime}}\right),\\
